### 2024-07-11 conteudo/background/linux.tex
Add more info required
do some things missed

The contributions to the Linux are coordinate with the usage of the Git source management tool. The contributions 
made to the project are formated as patches, which are text documents describing differences between two different 
versions of a source tree \citep{melissa}.

AMD Display Driver is a linux's subsystem responsible for the management of AMD GPU's. This subsystem have a problem 
with code clone duplication, which are acknowledged by the subsystem's maintainters. For this reason, we selected this
subsystem as the primary focus for refactoring the detected code clone duplication by our tool.
(MAYBE CHANGE TO: For this reason, we selected this subsystem as the primary focus for our empirical analysis in our research).

>>>>

The contributions to the Linux are coordinate with the usage of the Git source management tool. The contributions 
made to the project are formated as patches, which are text documents describing differences between two different 
versions of a source tree  The patches are sent and reviewed through the Linux mailing lists \citep{melissa}.

Mailing lists are the official means of communication of the Linux community, through the mailing lists the community members 
send and review
contributions to the kernel, discuss topics related to the Linux such as which new features to add, et cetera. 
As there are multiples
subsystems in the Linux kernel, there are multiples mailing lists in the Linux to organize the discussion made. Every subsystem 
have their own mailing list to concentrate the discussion related to the subsystem \citep{melissa}. The iteractions made in the
mailing lists are documented and stored in the Linux kernel Lore \citep{linuxlore}, which serves as a repository of the
discussion made in the Linux kernel to be consulted by anyone interested.

One the the Linux kernel subsystem is the AMD Display Driver, a subsystem responsible for implement the drivers required to enable
AMD GPU's work properly in the Linux environment. The maintainers of this subsystem reported a empirical problem they have in
the subsystem, which is a significant amount of duplicated code in the subsystem, a problem that hinders the maintainment of the
subsystem. This reported problem is the starting point that initiated our research, making the AMD Display Driver our principal
objecte of study to undertand how to mitigate duplicated code in the Linux kernel.

(I WANT TO CHANGE THE AMD DISPLAY paragraph, WHY DO I NEED TO CHANGE IT? I SHOULD ANOTATE WHAT I WANTED, I MADE A CHANGE
 TO MAKE IT BETTER BUT NOT SURE IF THERE IS SOME INFORMATION I WANTED TO PUT IN IT)

### 2024-07-11 conteudo/methods/methods.tex
Add a comment to approach later
do some things missed

On this section, we will describe a generic approach pipeline to mitigate code duplication found in the Linux kernel. Then we
will describe the methodology to select a subset of duplicated functions found by our tool and finally, describe the ethnographic
methodology to interact with the Linux community.

\subsection{Generic approach pipeline to mitigate code duplication}

@@

The figure (CREATE FIGURE AND ADD HERE) ilustrates the approach pipeline described in this section.

@@

@@

When we make a code duplication mitigation following our approach pipeline described in \citep{subsec:pipeline}, we are apt
to initiate our ethnographic research. We resorted to a participant-observation approach as our ethnographic methodology, where we 
will act as contributors of the Linux kernel to the AMD Display driver, interacting with the maintainers of the AMD Display driver
attempting to get our mitigations added to the Linux kernel.

>>>>

On this section, we will describe a generic systematic approach to mitigate code duplication found in the Linux kernel. Then we
will describe the methodology to select a subset of duplicated functions found by our tool and finally, describe the ethnographic
methodology to interact with the Linux community.

\subsection{Generic systematic approach to mitigate code duplication}

@@

The figure (CREATE FIGURE AND ADD HERE) ilustrates the systematic approach described in this section.

@@

(MAYBE I SHOULD ADD A RESTRICTION ABOUT IGNORING AUTOMATED GENERATED CODE, such as DML folder)

@@

When we make a code duplication mitigation following our systematic approach described in \ref{subsec:pipeline}, we are apt
to initiate our ethnographic research. We resorted to a participant-observation approach as our ethnographic methodology, where we 
will act as contributors of the Linux kernel to the AMD Display driver, interacting with the maintainers of the AMD Display driver
attempting to get our mitigations added to the Linux kernel.
